---
title: "List Scoring"
output:
  pdf_document: default
  word_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## First Steps 

NOTE: Your data needs to be in the folder where your code is located!

The first Chunk of Code will always do 3 Things for us

1) Clear ALL Variables (to make sure nothing is "left over") and clear the  screen. 
2) Read in the data we want to use. In our case the file is called "Data_List Scoring_R.csv"
3) Explore the data (what variables are in it and what are some basic statistics for these variables)


```{r}

# Clear All Variables & Clear Screen
rm(list=ls())
cat("\014")

# Read in the Data
data.list = read.csv("tfa_clean.csv")

# Explore the data
str(data.list)
summary(data.list)

```



## BINARY LOGIT MODEL 

We will run our model on the TRAINING Data (i.e, using the FIRST 200 IDs)

1) Define y (Dependent Variable). For this example, y_Response (a consumer either buys or not) is used

2) Define X (Independent Variables). For this example, x1_Gender, x2_Hotline1 and x3_Hotline2 are used

3) Run the Model. For example, a model where response (y_response) is a function of gender (x1_gender), Hotline1 (x2_Hotline1), and Hotline2 (x3_Hotline2)



```{r}

# Define TRAINING Data (i.e, using the FIRST 80% IDs)
data.training <- data.list[1:2056,]

# Run the Binary Logit Model (includes an INTERCEPT)
glm.model <- glm(Matriculated ~ RegionPrefLevel
+ RequestedRegionalReassignment
+ Ethnicity + Senior2007
+ CumulativeGPA
+ SpecialEducationPrefLevel
+ BilingualPreferred
+ Gender
+ ReceivedPellGrants
+ PrimarySubject
+ GradeLevel
+ Contacted
, family=binomial(link='logit'), data=data.training)

# Display Results
summary(glm.model)

```

## SCORING the TESTING Data 

Use the TESTING data (i.e., IDs 201-500 which are NOT used for estimation) to predict the buy/no buy decision for each of the 300 IDs in the TESTING sample


```{r}

# Define TESTING Data (i.e, IDs last 50%)
data.testing <- data.list[2057:2570,]

# Predicting Buy/No Buy for the 300 TESTING IDs based on the Model Estimates
(prediction.testing <- data.frame(ID = data.testing$PersonId, 
                                  BinaryLogitProbability = predict(glm.model, data.testing, type = c("response")),
                                  BinaryLogitPredict     = round(predict(glm.model, data.testing, type = c("response")), digits = 0)))

# Add Real Response
prediction.testing$Matriculated = data.testing$Matriculated

# Add Lift to the Forecast. Recall lift is simply the predicted response rate divided by the average response rate of the Training sample
prediction.testing$lift = prediction.testing$BinaryLogitProbability/mean(data.training$Matriculated)

# Prediciton of Number of Buyers
sum(prediction.testing["BinaryLogitPredict"])
sum(prediction.testing["BinaryLogitProbability"])

# Histogram of Props
hist(prediction.testing$BinaryLogitProbability, main = paste("Histogram of Matriculated Probs"), xlab = "Prob of Matriculated")

# Confusion Matrix
library(gmodels)
CrossTable(data.testing$Matriculated, prediction.testing$BinaryLogitPredict,prop.r=TRUE, prop.c=FALSE, prop.t=FALSE,
           prop.chisq=FALSE, dnn = c("Real Matriculated", "Predicted Matriculated"))


# Creating a Response Probability Chart
# First need to sort by response (best to worst), so we need to sort by "-probability" as it by default sort from smallest to largest
prediction.testing.ResponseSort <- prediction.testing[order(-prediction.testing$BinaryLogitProbability),]

# Exporting the Predictions to Excel
# You can open a csv file in xl
write.csv(prediction.testing.ResponseSort, file = "Prediction_TestingSort.csv")

# Now we can make a plot of the response rate by number of prospects targeted
plot(prediction.testing.ResponseSort$BinaryLogitProbability, main="Marginal Matriculate Rate",
   xlab="#Prospects", ylab="Matriculate Rate")

# Expected Responses
best.model <-data.frame(matrix(ncol = 2, nrow = 1))

CumulativeSum <-data.frame(matrix(ncol = 2, nrow = 514))
CumulativeSum$Matriculate_predicted = cumsum(prediction.testing.ResponseSort$BinaryLogitProbability)
CumulativeSum$Matriculate_real = cumsum(prediction.testing.ResponseSort$Matriculated)

plot(CumulativeSum$Matriculate_predicted,
ylim =c(0, 500),
main="number of predicted matriculated vs. number of real matriculated",
xlab="#Prospects", ylab="total number of martriculated",
type="l",
col="blue")
lines(CumulativeSum$Matriculate_real, col="green")
legend("bottomright",
c("Predicted Matriculated","Real Matriculated"),
fill=c("blue","green")
)

```



